\documentclass[main.tex]{subfiles}
\begin{document}
I am grateful for the mentorship, teaching, and patience of my advisor Greg Hirth.  A marriage of materials science and geology has not always been easy, but his thoughtfulness and talent has carried us through. Thank you for believing in my ability execute unusual projects, like building a laser interferometer.

I would like to thank my committee members for sage guidance over my career. Reid Cooper, Chris Huber, Yan Liang, and Marc Parmentier have all supported me at times at times when I was struggling with lab or numerical problems. Nicolas Brantut and Matej Pec have been invaluable in their guidance through laboratory challenges, particularly during creep testing. David Kohlstedt invited me into the world of rock deformation at a time when I was discarded by materials science, and I will be forever grateful for that.

I would also like to thank my colleagues in the rock deformation lab. You have made coming to work every day an exciting experience. Thank you also for your patience as I have written control software and upgraded the electronics on the Griggs rigs.

I would like to thank all of the faculty, staff, undergraduates, and graduate students. I have 
really enjoyed my time here at Brown University being a part of this community. The friendly and collegial atmosphere has made me a better scientist.

Finally, I'd like to thank my family Barb, Steve, and Lisa Burdette for supporting me along my journey to this point. Yaruska Ordinola-Perez in particular has helped me stay grounded, motivated, and inspired me to be a better person. Thank you all again for your support.

\end{document}